Full Brain Blood-Oxygen-Level-Dependent Signal \\ Parameter Estimation using Sequential Monte Carlo Methods

### 2010-08-21 doc/presentation/main.tex
Work on the first few slides

\documentclass{beamer}
\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5]{beamerposter}

@@

\section{Background}
\begin{frame}{The BOLD Response}
\begin{figure}
\includegraphics[scale=.23]{model}
\caption{
    \tiny
    \cite{nonlinearfiltering}
}
\end{figure}
\end{frame}

@@

\section{Nonlinear Regression}
\begin{frame}{Equations}
  \begin{itemize}
    \item Normalized Cerebral Blood Flow:
    $$\ddot{f}(t) = \epsilon u(t) - \dot{f}(t)/\tau_s - (f(t)/\tau_f - 1)$$
    \item Normalized Cerebral Blood Volume:
    $$\dot{v}(t) = (1/\tau_0)( f(t) - v(t) ^ {1/\alpha}) $$
    \item Normalized Deoxyhaemoglobin Content:
    $$\dot{q}(t) = \frac{1}{\tau_0}\left(\frac{f(t)(1- (1-E_0)^{1/f(t)})}{E_0} - 
            \frac{q(t)}{v(t)^{1-1/\alpha}}\right)$$
    \item Hemodynamic Response - BOLD Signal
    $$y(t) = V_0(a_1( 1 - Q(t)) - a_2(1 - V(t)))$$
  \end{itemize}
\end{frame}

>>>>

\documentclass{beamer}
%\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5]{beamerposter} 
%\setbeameroption{show notes on second screen}

@@

\section{Introduction}
\begin{frame}{Balloon Model}
\begin{figure}
\includegraphics[scale=.23]{model}
\caption{
    \tiny
    \cite{nonlinearfiltering}
}
\end{figure}
\note{Rates range from below 1 Hz to 5 to 6 Hundred Hz}
\note{Change in average firing rates increase metabolism and sympathetic response causes
        increased inflow of oxygenated blood.}
\note{In the version of the Balloon model I used, the flow is locked to metabolism.}
\note{According the balloon model this increases the local blood volume, and the outflow pressure.}
\note{So the signal is altered by changes in the ratio of Deoxyhemoglobin and Oxygenated Hemoglobin,
        which are a function of Volume and Oxygenation.}
\end{frame}

\begin{frame}{Equations}
  \begin{itemize}
    \item Flow Inducing Signal
    $$\dot{s}(t) = \epsilon u(t) - s(t)/\tau_s - (f(t)/\tau_f - 1)$$
    \item Normalized Cerebral Blood Inflow:
    $$\dot{f}(t) = s $$
    \item Normalized Cerebral Blood Volume:
    $$\dot{v}(t) = (1/\tau_0)( f(t) - v(t) ^ {1/\alpha}) $$
    \item Normalized Deoxyhaemoglobin Content:
    $$\dot{q}(t) = \frac{1}{\tau_0}\left(\frac{f(t)(1- (1-E_0)^{1/f(t)})}{E_0} - 
            \frac{q(t)}{v(t)^{1-1/\alpha}}\right)$$
    \item Hemodynamic Response - BOLD Signal
    $$y(t) = V_0(a_1( 1 - Q(t)) - a_2(1 - V(t)))$$
  \end{itemize}
  \note{System is dissipative:}
  \note{If no input is provided, it will rather quickly decay.}
  \note{Constant input leads to steady state response.}
  \note{First term in $\dot{q}$ is the metabolism term}
  \note{Outflow is the $v^{1/\alpha}$ term
  \note{Significant nonlinearity.}
\end{frame}

\begin{frame}{Solutions: Approximate Method}
  \begin{itemize}
    \item Canonical Hemodynamic Response Function
    \note{Linear Approximation}
    \begin{itemize}
        \item Maximum Likelihood Possible
        \item Inflexible - even to changes in onset time
    \end{itemize}

    \item Volterra Kernel 
    \note{Quadratic Approximation}
    \begin{itemize}
        \item Quadratic Convolution used to approximate Jacobian Matrix.
        \note{Because of the nonlinearities in the BOLD model, step size for
                integrating would otherwise be extremely small}
        \item Volterra approximation quality is not known.
        \note{Its possible this isn't even know-able}
    \end{itemize}
    \note{Volterra Approximation depends on sparsity etc}
  \end{itemize}
    \begin{center}
    \includegraphics[width=10cm,height=4cm]{HRF}
    \end{center}
\end{frame}

@@

\section{Nonlinear Regression}
